{\itshape The geography of urban boundaries in Great Britain from the network of Twitter user spatial interactions}

### 2016-05-03 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
new line

\section{Related Work}

@@

\begin{thebibliography}{9}

\markboth{}{International Journal of Geographical Information Science}

\bibitem[\protect\citeauthoryear{Brockmann {\itshape{et~al.}}}{2006}]{brockmann2006}
Brockmann, D., Hufnagel, L., Geisel, T., 2006. The scaling laws of human travel. Nature 439, 462–5. doi:10.1038/nature04292

\bibitem[\protect\citeauthoryear{Clauset {\itshape{et~al.}}}{2009}]{clauset2009}
Clauset, A., Shalizi, C., Newman, M., 2009. Power-Law Distributions in Empirical Data. Society for Industrial and Applied Mathematics Review. 51, 661–703. doi:10.1137/070710111

\bibitem[\protect\citeauthoryear{Coscia {\itshape{et~al.}}}{2011}]{coscia2011}
Coscia, M., Giannotti, F., Pedreschi, D., 2011. A Classification for Community Discovery Methods in Complex Networks. Statistical Analysis and 
\bibitem[\protect\citeauthoryear{De Domenico {\itshape{et~al.}}}{2015}]{domenico2015}
De Domenico, M., Lancichinetti, A., Arenas, A., Rosvall, M., 2015. Identifying Modular Flows on Multilayer Networks Reveals Highly Overlapping Organization in Interconnected Systems. Physical Review X, 5. doi:10.1103/PhysRevX.5.011027

\bibitem[\protect\citeauthoryear{Fortunato and Barthélemy}{2007}]{fortunato2007}
Fortunato, S., Barthélemy, M., 2007. Resolution limit in community detection. Proceedings of the National Academy of Sciences, 104, 36–41. doi:10.1073/pnas.0605965104

\bibitem[\protect\citeauthoryear{González {\itshape{et~al.}}}{2008}]{gonzalez2008}
González, M.C., Hidalgo, C.A., Barabási, A.-L., 2008. Understanding individual human mobility patterns. Nature, 453, 779–82. doi:10.1038/nature06958

@@

\bibitem[\protect\citeauthoryear{Hawelka {\itshape{et~al.}}}{2014}]{hawelka}
Hawelka, B., Sitko, I., Beinat, E., Sobolevsky, S., Kazakopoulos, P., Ratti, C., 2014. Geo-located Twitter as proxy for global mobility patterns. Cartography and Geographic Information Science, 41, 260–271. doi:10.1080/15230406.2014.890072

\bibitem[\protect\citeauthoryear{Jiang and Miao}{2015}]{jiang2015}
Jiang, B., Miao, Y., 2015. The evolution of natural cities from the perspective of location-based social media. The Professional Geographer, 67(2), 295-306.

@@

\bibitem[\protect\citeauthoryear{Liu {\itshape{et~al.}}}{2015}]{liu2015}
Liu, X., Gong, L., Gong, Y., Liu, Y., 2015. Revealing travel patterns and city structure with taxi trip data. J. Transportation Geography, 43, 78–90. doi:10.1016/j.jtrangeo.2015.01.016

@@

\bibitem[\protect\citeauthoryear{Long {\itshape{et~al.}}}{2015}]{long2015}
Long, Y., Han, H., Tu, Y., Shu, X., 2015. Evaluating the effectiveness of urban growth boundaries using human mobility and activity records. Cities, 46, 76-84.

@@

\bibitem[\protect\citeauthoryear{Newman}{2006}]{newman2006}
Newman, M.E.J., 2006. Modularity and community structure in networks. Proceedings of the National Academy of Sciences, 103, 8577–82. doi:10.1073/pnas.0601602103

@@

\bibitem[\protect\citeauthoryear{Reynolds}{2012}]{reynolds2012}
Reynolds, A., 2012. Truncated levy walks are expected beyond the scale of data collection when correlated random walks embody observed movement patterns. Journal of The Royal Society Interface, 9(68), 528-534.

\bibitem[\protect\citeauthoryear{Rhee {\itshape{et~al.}}}{2011}]{rhee2011}
Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S. J., and Chong, S., 2011. On the levy-walk nature of human mobility. IEEE/ACM transactions on networking (TON), 19(3), 630-643.

\bibitem[\protect\citeauthoryear{Rinzivillo {\itshape{et~al.}}}{2012}]{rinzivillo2012}
Rinzivillo, S., Mainardi, S., Pezzoni, F., Coscia, M., Pedreschi, D., Giannotti, F., 2012. Discovering the Geographical Borders of Human Mobility. KI - Künstl. Intell. 26, 253–260. doi:10.1007/s13218-012-0181-8

\bibitem[\protect\citeauthoryear{Rosvall {\itshape{et~al.}}}{2010}]{rosvall2010}
Rosvall, M., Axelsson, D., Bergstrom, C.T., 2010. The map equation. The European Physical Journal Special Topics, 178, 13–23. doi:10.1140/epjst/e2010-01179-1

\bibitem[\protect\citeauthoryear{Rosvall and Bergstrom}{2008}]{rosvall2008}
Rosvall, M., Bergstrom, C.T., 2008. Maps of random walks on complex networks reveal community structure. Proceedings of the National Academy of Sciences, 105, 1118–1123.

\bibitem[\protect\citeauthoryear{Sakaki {\itshape{et~al.}}}{2010}]{sakaki2010}
Sakaki, T., Okazaki, M., Matsuo, Y., 2010. Earthquake Shakes Twitter Users: Real-time Event Detection by Social Sensors, in: Proceedings of the 19th International Conference on World Wide Web, WWW ’10. ACM, New York, NY, USA, pp. 851–860. doi:10.1145/1772690.1772777

@@

\bibitem[\protect\citeauthoryear{Simini {\itshape{et~al.}}}{2012}]{simini2012}
Simini, F., González, M. C., Maritan, A., Barabási, A. L., 2012. A universal model for mobility and migration patterns. Nature, 484(7392), 96-100.

@@

@@

\bibitem[\protect\citeauthoryear{Zandbergen}{2009}]{zandbergen2009}
Zandbergen, P.A., 2009. Accuracy of iPhone Locations: A Comparison of Assisted GPS, WiFi and Cellular Positioning. Transactions in GIS, 13, 5–25. doi:10.1111/j.1467-9671.2009.01152.x

@@

\bibitem[\protect\citeauthoryear{Zhong {\itshape{et~al.}}}{2014}]{zhong2014}
Zhong, C., Arisona, S.M., Huang, X., Batty, M., Schmitt, G., 2014. Detecting the dynamics of urban structure through spatial network analysis. International Journal of Geographical Information Science, 28, 2178–2199. doi:10.1080/13658816.2014.914521

>>>>

\section{Background and Related Work}

@@

\begin{thebibliography}{9}
\markboth{}{International Journal of Geographical Information Science}

\bibitem[\protect\citeauthoryear{Brockmann {\itshape{et~al.}}}{2006}]{brockmann2006}
Brockmann, D., Hufnagel, L., Geisel, T., 2006. The scaling laws of human travel. Nature 439, pp. 462-465. doi:10.1038/nature04292

\bibitem[\protect\citeauthoryear{Clauset {\itshape{et~al.}}}{2009}]{clauset2009}
Clauset, A., Shalizi, C., Newman, M., 2009. Power-Law Distributions in Empirical Data. Society for Industrial and Applied Mathematics Review. 51, pp. 661-703. doi:10.1137/070710111

\bibitem[\protect\citeauthoryear{Coscia {\itshape{et~al.}}}{2011}]{coscia2011}
Coscia, M., Giannotti, F. and Pedreschi, D., 2011. A classification for community discovery methods in complex networks. Statistical Analysis and Data Mining, 4(5), pp. 512-546.

\bibitem[\protect\citeauthoryear{De Domenico {\itshape{et~al.}}}{2015}]{domenico2015}
De Domenico, M., Lancichinetti, A., Arenas, A., Rosvall, M., 2015. Identifying Modular Flows on Multilayer Networks Reveals Highly Overlapping Organization in Interconnected Systems. Physical Review X, 5. doi:10.1103/PhysRevX.5.011027

\bibitem[\protect\citeauthoryear{Fortunato and Barthélemy}{2007}]{fortunato2007}
Fortunato, S., Barthélemy, M., 2007. Resolution limit in community detection. Proceedings of the National Academy of Sciences, 104, pp. 36-41. doi:10.1073/pnas.0605965104

\bibitem[\protect\citeauthoryear{Gao {\itshape{et~al.}}}{2014}]{gao2014}
Gao, S., Yang, J.A., Yan, B., Hu, Y., Janowicz, K. and McKenzie, G., 2014. Detecting Origin-Destination Mobility Flows From Geotagged Tweets in Greater Los Angeles Area. In Eighth International Conference on Geographic Information Science (GIScience'14).

\bibitem[\protect\citeauthoryear{González {\itshape{et~al.}}}{2008}]{gonzalez2008}
González, M.C., Hidalgo, C.A., Barabási, A.-L., 2008. Understanding individual human mobility patterns. Nature, 453, pp. 779-782. doi:10.1038/nature06958

@@

\bibitem[\protect\citeauthoryear{Hawelka {\itshape{et~al.}}}{2014}]{hawelka}
Hawelka, B., Sitko, I., Beinat, E., Sobolevsky, S., Kazakopoulos, P., Ratti, C., 2014. Geo-located Twitter as proxy for global mobility patterns. Cartography and Geographic Information Science, 41, pp. 260-271. doi:10.1080/15230406.2014.890072

\bibitem[\protect\citeauthoryear{Huang {\itshape{et~al.}}}{2016}]{huang2016}
Huang, Q. and Wong, D.W., 2016. Activity patterns, socioeconomic status and urban spatial structure: what can social media data tell us?. International Journal of Geographical Information Science, pp.1-26.

\bibitem[\protect\citeauthoryear{Jiang and Miao}{2015}]{jiang2015}
Jiang, B., Miao, Y., 2015. The evolution of natural cities from the perspective of location-based social media. The Professional Geographer, 67(2), pp. 295-306.

@@

@@

\bibitem[\protect\citeauthoryear{Liu {\itshape{et~al.}}}{2015}]{liu2015}
Liu, X., Gong, L., Gong, Y., Liu, Y., 2015. Revealing travel patterns and city structure with taxi trip data. J. Transportation Geography, 43, pp. 78-90. doi:10.1016/j.jtrangeo.2015.01.016

\bibitem[\protect\citeauthoryear{Liu {\itshape{et~al.}}}{2015}]{liu2014}
Liu, Y., Sui, Z., Kang, C., Gao, Y., 2014. Uncovering patterns of inter-urban trip and spatial interaction from social media check-in data. PLoS ONE, 9(1), p.e86026.

\bibitem[\protect\citeauthoryear{Long {\itshape{et~al.}}}{2015}]{long2015}
Long, Y., Han, H., Tu, Y., Shu, X., 2015. Evaluating the effectiveness of urban growth boundaries using human mobility and activity records. Cities, 46, pp. 76-84.

\bibitem[\protect\citeauthoryear{Long {\itshape{et~al.}}}{2015}]{long2015}
Luo, F., Cao, G., Mulligan, K., Li, X., 2016. Explore spatiotemporal and demographic characteristics of human mobility via Twitter: A case study of Chicago, Applied Geography, 70, pp. 11-25

@@

\bibitem[\protect\citeauthoryear{Newman}{2006}]{newman2006}
Newman, M.E.J., 2006. Modularity and community structure in networks. Proceedings of the National Academy of Sciences, 103, pp. 8577-8582. doi:10.1073/pnas.0601602103

@@

\bibitem[\protect\citeauthoryear{Reynolds}{2012}]{reynolds2012}
Reynolds, A., 2012. Truncated levy walks are expected beyond the scale of data collection when correlated random walks embody observed movement patterns. Journal of The Royal Society Interface, 9(68), pp. 528-534.

\bibitem[\protect\citeauthoryear{Rhee {\itshape{et~al.}}}{2011}]{rhee2011}
Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S. J., and Chong, S., 2011. On the levy-walk nature of human mobility. IEEE/ACM transactions on networking (TON), 19(3), pp. 630-643.

\bibitem[\protect\citeauthoryear{Rinzivillo {\itshape{et~al.}}}{2012}]{rinzivillo2012}
Rinzivillo, S., Mainardi, S., Pezzoni, F., Coscia, M., Pedreschi, D., Giannotti, F., 2012. Discovering the Geographical Borders of Human Mobility. KI - Künstl. Intelligenz, 26, pp. 253-260. doi:10.1007/s13218-012-0181-8

\bibitem[\protect\citeauthoryear{Rosvall {\itshape{et~al.}}}{2010}]{rosvall2010}
Rosvall, M., Axelsson, D., Bergstrom, C.T., 2010. The map equation. The European Physical Journal Special Topics, 178, pp. 13–23. doi:10.1140/epjst/e2010-01179-1

\bibitem[\protect\citeauthoryear{Rosvall and Bergstrom}{2008}]{rosvall2008}
Rosvall, M., Bergstrom, C.T., 2008. Maps of random walks on complex networks reveal community structure. Proceedings of the National Academy of Sciences, 105, pp. 1118-1123.

\bibitem[\protect\citeauthoryear{Sakaki {\itshape{et~al.}}}{2010}]{sakaki2010}
Sakaki, T., Okazaki, M., Matsuo, Y., 2010. Earthquake Shakes Twitter Users: Real-time Event Detection by Social Sensors, in: Proceedings of the 19th International Conference on World Wide Web, WWW ’10. ACM, NY, USA, pp. 851-860

@@

\bibitem[\protect\citeauthoryear{Simini {\itshape{et~al.}}}{2012}]{simini2012}
Simini, F., González, M. C., Maritan, A., Barabási, A. L., 2012. A universal model for mobility and migration patterns. Nature, 484(7392), pp. 96-100.

@@

\bibitem[\protect\citeauthoryear{Steiger {\itshape{et~al.}}}{2015}]{steiger2015}
Steiger, E., Westerholt, R., Resch, B. and Zipf, A., 2015. Twitter as an indicator for whereabouts of people? Correlating twitter with uk census data. Computers, Environment and Urban Systems, 54, pp. 255-265.

@@

\bibitem[\protect\citeauthoryear{Zandbergen}{2009}]{zandbergen2009}
Zandbergen, P.A., 2009. Accuracy of iPhone Locations: A Comparison of Assisted GPS, WiFi and Cellular Positioning. Transactions in GIS, 13, pp. 5-25. doi:10.1111/j.1467-9671.2009.01152.x

@@

\bibitem[\protect\citeauthoryear{Zhong {\itshape{et~al.}}}{2014}]{zhong2014}
Zhong, C., Arisona, S.M., Huang, X., Batty, M., Schmitt, G., 2014. Detecting the dynamics of urban structure through spatial network analysis. International Journal of Geographical Information Science, 28, pp. 2178-2199, doi:10.1080/13658816.2014.914521
